Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-07-04 Silvers_cfmip.tex
changes to Silvers_cfmip.tex, minor changes to Silvers_cfmip_extraTable.tex, and Silvers_cfmip_CRE_SinglePanel.tex

We compare output from the AM4.0 GCM to observations from ISCCP, MISR, MODIS, CALIPSO, and CERES-EBAF.
For details of the data used see Table 2.

@@

Due to a combination of changing computing power and differing objectives, the sensitivity of Earth's climate to 
perturbations has been estimated in many different ways over the past few decades.  
We have computed the climate feedback parameter that appears in Table 1 with multiple methods.  
Three common methods are briefly described here.  
First, the climate sensitivity can be estimated from the change in radiative flux at the top of the 
atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990).  
Second, the climate
sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
instantaneously quadrupled relative to the pre-Industrial values.  Linear regression can then be used to 
estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
and used by the IPCC.  Third, the climate sensitivity
can be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
$\rm{CO}_{2}$ concentration.   This method is used to define the Transient Climate Response (TCR).
For a particular climate model, the only way to be sure of the climate sensitivity is to run the 
coupled model after a perturbation has been applied and wait until the model has fully 
equilibrated.  Evidence indicates that this takes thousands of years of 
simulation (Stouffer, 2004; Li et al., 2012; Paynter et al., 2018; Rugenstein et al., 2019).
Because of the limiting cost of such long experiments, determining an accurate measure 
of the climate sensitivity to perturbations from a simulation that is not fully equilibrated is an 
essential component of climate science.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).  The \textit{amip p8K} is not a separate experiment but
shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
    \begin{tabular}{*{8}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
    \\
    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11          & 0.65   & -0.30  \\  
    \\
    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10          & 0.14  & 0.02    \\  
    \\
    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21         & 0.5  & -0.32       \\  
    \\
    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03         & -1.7   & -1.94      \\  
    \\
    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30          & 0.6    & 0.76        \\  \hline

@@

The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
differences in the measures of sensitivity reveal important details of the physics that underly the response
of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
experiments are the historical simulation (\textit{historical}: years 1850-2014),  the abrupt quadrupling of 
$\rm{CO}_2$ concentration (\textit{abrupt-4xCO$_2$}: 300 years for this paper), and the experiment in 
which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: 150 years, doubling at year 70).  
The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
observed historical record.  This has frequently been used to estimate the climate sensitivity using the 
energy budget method 
(Otto et al., 2013, Armour et al., Andrews et al., \citeA{Winton_etal_2020}; Lewis and Curry?).  
The \textit{abrupt-4xCO$_2$} experiment has been utilized by the IPCC to derive measures of the 
ECS among the CMIP5 and CMIP6 models using a linear regression of the change in TOA radiative fluxes 
and surface air temperature over the first 150 years of the response to the increase in $CO_2$ 
concentration (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
$\rm{CO}_2$ concentration, the \textit{1pctCO2} is an experiment of the Earth system when 
there is a  1 \% per year increase of the $\rm{CO}_2$ concentration until it is doubled relative to the 
pre-Industrial values.  The sensitivity at the point of doubling is defined 
as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
will reach (insert 2xCO2 value) around the middle of this century.

The radiative feedbacks at the TOA were computed for a collection of CMIP5 models by Ringer et al., 2014.  
The results from that study provide a convenient point of reference for our findings.  
Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models.  
That is, for the coupled abrupt $4xCO_{2}$ experiment, feedbacks are computed as  
the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
(\cite{Gregory_etal_2004}; Andrews et al., 2012).  For the atmosphere only experiments 
(\textit{amip-p4K, amip-m4K, amipFuture}, and \textit{aqua-p4K}), the feedbacks are calculated as the 
differences in TOA flux anomalies between the perturbation and control experiments, normalized 
by the change in surface air temperature.  In addition, we include values that have been computed from the 
\textit{1pctCO2} experiment.   Positive values indicate a feedback that leads to warming of the climate system.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
  shows (in black) the measured CRE from two versions of the CERES-EBAF observations.   compared to 
  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown at left is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (1950-2014),
  \textit{abrupt-4xCO$_2$} (101-150), and \textit{1pctCO$_2$} (101-150)) and the AM4.0 amip experiment.  Right panel, the CRE feedback from four 
  of the amip-like experiments from CFMIP.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback 
(-0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$, climate feedback parameter?) that results from differences in 
both the cloudy and clear sky fluxes.   The LW CLR feedback is nearly constant between the 
aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   The SW CLR 
feedback is nearly constant across the \textit{amip} experiments but varies significantly
between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
The relatively large range of the SW CRE (either 0.58 $\rm{W m^{-2}K^{-1}}$ or 1.15 $\rm{W m^{-2}K^{-1}}$)
confirms the important role played by mid- and low-level clouds outside of the region of 
deep tropical convection where the LW and SW effects of clouds largely cancel each other.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CF_figure9.pdf}
  \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the middle column
  shows values relative to the PI control experiment and the right column
  shows values relative to the \textit{amip} experiment.  For the coupled model experiments
 \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted while for the 
 \textit{historical} experiment the years 1950-2014 are used.  
  For reference cloud fraction from the 
 \textit{historical} (purple) and \textit{amip} are also shown.}
  \label{fig:CF_warming}
\end{figure}

@@

 \begin{table}
\begin{center}
\caption{Experiments used.   Should I list the years the experiment simulate or just the years used in the analysis?}
    \begin{tabular}{*{4}{c}}
    \hline
    \hline
 Experiment & Class & Configuration & Years   \\ \hline
    historical        &   DECK      &  atmosphere \& ocean   &  Jan 1950 -Dec 2014               \\ 
    \\
    abrupt 4xCO2   & DECK       &  atmosphere \& ocean       & 150 years  \\  
    \\
    1pct CO2   & DECK        &  atmosphere \& ocean  & 150 years \\  
    \\
    PI Control  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
    \\
    amip  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
    \\
    amip +4K  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
    amip -4K   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
    amip Future 4K  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
    aqua control        & CFMIP  & atmosphere  & 10 years \\
    aqua +4K.  & CFMIP    & atmosphere  &  10 years \\ \hline

 \begin{sidewaystable}
 \caption{ Observational Data Sets Used in This Paper}
 \centering
 \begin{tabular}{l l}
 \hline
 Data  & Description  \\
 \hline
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed2.8   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 2.8  \\
                                     & Reference: Loeb et al. (2009); Smith et al. (2011).  \\
                                     & URL: \url{http://ceres.larc.nasa.gov/documents/DQ_summaries/CERES_EBAF_Ed2.8_DQS.pdf}.   \\
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed4.1   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 4.1  \\
                                     & Reference:   \\
                                     & URL: \url{http://ceres.larc.nasa.gov}.   \\
   Cloud amount and optical depth (dates) & Short name:  MISR   \\
                                                                   &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: MODIS  \\
                                                                   & Long name: Moderate Resolution Imaging Spectroradiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: ISCCP   \\
                                                                   & Long name: International Satellite Cloud Climatology Project   \\
                                                                   & Reference: Rossow and Schiffer (1991); Pincus et al. (2012)   \\
                                                                   & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
   Cloud amount  & Short name: CALIPSO   \\
                           & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\
                           & Reference: Chepfer et al. (2010); Cesana and Chepfer (2013)      \\
    \hline
 \multicolumn{2}{l}{$^{a}$Footnote text here.}
 \end{tabular}
 \end{sidewaystable}

>>>>

We compare output from the AM4.0 GCM to observations from ISCCP, MISR, MODIS, CALIPSO, and CERES-EBAF.
More details are provided in the appendix.  The CMIP6 and CFMIP experiments used in this study are given in Table
\ref{tab:exps} and the observational data sets used are given in Table \ref{tab:obs}.

@@

Due to a combination of changing computing power and differing objectives, the sensitivity of Earth's climate to 
perturbations has been estimated in many different ways over the past few decades.  
We have computed the climate feedback parameter that appears in Table 1 with multiple methods.    
The climate sensitivity can be estimated from the change in radiative flux at the top of the 
atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990).  
Additionally, the climate
sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
instantaneously increased relative to the pre-Industrial values.  Linear regression can then be used to 
estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
and used by the IPCC.  The climate sensitivity
can also be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
$\rm{CO}_{2}$ concentration.   This method is used to define the Transient Climate Response (TCR).
For a particular climate model, the only way to be sure of the climate sensitivity is to run the 
coupled model after a perturbation has been applied and wait until the model has fully 
equilibrated.  Evidence indicates that this takes thousands of years of 
simulation (Stouffer, 2004; Li et al., 2012; Paynter et al., 2018; Rugenstein et al., 2019).
Because of the limiting cost of such long experiments, determining an accurate measure 
of the climate sensitivity to perturbations from a simulation that is not fully equilibrated is an 
essential component of climate science.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux.   The \textit{amip p8K} is not a separate experiment but
shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
    \begin{tabular}{*{6}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future   \\ \hline
    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84           \\ 
    \\
    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11            \\  
    \\
    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10             \\  
    \\
    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21            \\  
    \\
    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03            \\  
    \\
    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30             \\  \hline

@@

The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
differences in the measures of sensitivity reveal important details of the physics that underly the response
of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
experiments are the historical simulation (\textit{historical}: years 1850-2014),  the abrupt quadrupling of 
$\rm{CO}_2$ concentration (\textit{abrupt-4xCO$_2$}: 300 years for this paper), and the experiment in 
which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: total of 150 years, doubling at year 70).  
The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
observed historical record.  This has frequently been used to estimate the climate sensitivity using the 
energy budget method 
(Otto et al., 2013, Armour et al., Andrews et al., \citeA{Winton_etal_2020}; Lewis and Curry?).  
The \textit{abrupt-4xCO$_2$} experiment has been utilized by the IPCC to derive measures of the 
ECS among the CMIP5 and CMIP6 models using a linear regression of the change in TOA radiative fluxes 
and surface air temperature over the first 150 years of the response to the increase in $CO_2$ 
concentration (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
$\rm{CO}_2$ concentration, the \textit{1pctCO2} is an experiment of the Earth system when 
there is a  1 \% per year increase of the $\rm{CO}_2$ concentration until it is doubled relative to the 
pre-Industrial values.  The sensitivity at the point of doubling is defined 
as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
will reach (insert 2xCO2 value) around the middle of this century.

The radiative feedbacks at the TOA were computed for a collection of CMIP5 models by Ringer et al., 2014.  
The results from that study provide a convenient point of reference for our findings.  
Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models in Table \ref{tab:lambda}.  
That is, for the coupled abrupt $4xCO_{2}$ experiment, feedbacks are computed as  
the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
(\cite{Gregory_etal_2004}; Andrews et al., 2012).  For the atmosphere only experiments 
(\textit{amip-p4K, amip-m4K, amipFuture}, and \textit{aqua-p4K}), the feedbacks are calculated as the 
differences in TOA flux anomalies between the perturbation and control experiments, normalized 
by the change in surface air temperature.  In addition, we include values that have been computed from the 
\textit{1pctCO2} experiment.   Positive values indicate a feedback that leads to warming of the climate system.

\begin{figure}
  \centering
  %\includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \includegraphics[width=0.75\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  The top panel 
  shows (black) the CRE from two versions of the CERES-EBAF observations compared to 
  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown in the top panel is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (yrs. 1950-2014),
  \textit{abrupt-4$\times$CO2} (yrs. 101-150), and \textit{1pctCO2} (yrs. 101-150)).  The middle panel shows an estimate of the 
  CRE feedback of the data in the top panels, computed by normalized according to the warming of surface air temperature over 
  the relevant time period.  The bottom panel shows the CRE feedback from four 
  CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}).  The sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback parameter 
($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in 
both the cloudy and clear sky fluxes.   The LW CLR feedback is nearly constant between the 
aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   The SW CLR 
feedback is nearly constant across the \textit{amip} experiments but varies significantly
between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
The relatively large range of the SW CRE (either 0.58 $\rm{W m^{-2}K^{-1}}$ or 1.15 $\rm{W m^{-2}K^{-1}}$)
confirms the important role played by mid- and low-level clouds outside of the region of 
deep tropical convection where the LW and SW effects of clouds largely cancel each other.

@@

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux.  The values for the Abrupt 4x$\rm{CO}_2^{a}$ experiment
have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).}
    \begin{tabular}{*{6}{c}}
    \hline
    \hline
 Feedback   &    Abrupt 4x$\rm{CO}_2^{a}$   &  Abrupt 4x$\rm{CO}_2^{b}$  & 1pct$CO_2$   & Historical    &  Amip   \\ \hline
    Net $\alpha$    &     -0.46     &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
    \\
    Net CRE  &    0.65    & -0.06       &  -0.26          & -0.45         & -0.46           \\  
    \\
    LW CRE    &   0.14       & 0.14        &  0.10            & -0.14           & -0.03          \\  
    \\
    SW CRE  &    0.5     &    -0.20       &  -0.26            & -0.31          & -0.43         \\  
    \\
    LW CLR   &   -1.7     &  -1.70       &  -1.71            & -1.94           & -2.25        \\  
    \\
    SW CLR  &      0.6         &   0.65        & 0.65              & 0.56             & 0.91          \\  
    \\
    $\Delta \rm{T}_s$     &     ?     & 3.99        &  ??                & 0.8              & 0.76          \\  \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:lambdahist}
\end{center}
\end{table}

It is also instructive to examine the values of the climate feedback parameter that result from simulations of 
recent decades.  In Table \ref{tab:lambdahist} we calculate the feedbacks for the coupled and amip experiments 
using   the difference in surface temperature  
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.
\begin{equation}
  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
\end{equation}
\begin{equation}
  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
\end{equation}

In the above equations $F_{4xCO_2}=N_{4xCO2}-N_{PiC}$; $F_{hist}=N_{hist(1996-2014)}-N_{PiC}$; 
$F_{1pctCO_2}=0.79F_{4xCO2}$.  The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  
%In all cases the years used for $N$ and $T$ are the same.  
$N_1$ and $T_1$ corresponds to years 101-150, while $N_2$ and $T_2$ corresponds to years 1996-2015.  
The relatively small span of years for $T_2$ were chosen to avoid the impact of volcanic behavior in the early 1990's that if included
complicate the interpretation of the climate feedback.  Feedbacks thus calculated are given in Table \ref{tab:lambdahist}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CF_figure9.pdf}
  \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the middle column
  shows values relative to the \textit{piControl} experiment and the right column
  shows values relative to the \textit{amip} experiment.  For the coupled model experiments
 \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted while for the 
 \textit{historical} experiment the years 1950-2014 are used.  
  For reference cloud fraction from the 
 \textit{historical} (purple) and \textit{amip} are also shown.}
  \label{fig:CF_warming}
\end{figure}

@@

 \begin{table}
\begin{center}
\caption{Experiments used.   Should I list the years the experiment simulate or just the years used in the analysis?}
    \begin{tabular}{*{4}{c}}
    \hline
    \hline
 Experiment & Class & Configuration & Years   \\ \hline
    historical        &   DECK      &  atmosphere \& ocean   &  Jan 1950 -Dec 2014               \\ 
    \\
    abrupt 4xCO2   & DECK       &  atmosphere \& ocean       & 150 years  \\  
    \\
    1pct CO2   & DECK        &  atmosphere \& ocean  & 150 years \\  
    \\
    piControl  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
    \\
    amip  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
    \\
    amip +4K  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
    amip -4K   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
    amip Future 4K  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
    aqua control        & CFMIP  & atmosphere  & 10 years \\
    aqua +4K.  & CFMIP    & atmosphere  &  10 years \\ \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:exps}
\end{center}
\end{table}

 \begin{sidewaystable}
 \caption{ Observational Data Sets Used in This Paper}
 \centering
 \begin{tabular}{l l}
 \hline
 Data  & Description  \\
 \hline
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed2.8   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 2.8  \\
                                     & Reference: Loeb et al. (2009); Smith et al. (2011).  \\
                                     & URL: \url{http://ceres.larc.nasa.gov/documents/DQ_summaries/CERES_EBAF_Ed2.8_DQS.pdf}.   \\
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed4.1   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 4.1  \\
                                     & Reference:   \\
                                     & URL: \url{http://ceres.larc.nasa.gov}.   \\
   Cloud amount and optical depth (dates) & Short name:  MISR   \\
                                                                   &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: MODIS  \\
                                                                   & Long name: Moderate Resolution Imaging Spectroradiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: ISCCP   \\
                                                                   & Long name: International Satellite Cloud Climatology Project   \\
                                                                   & Reference: Rossow and Schiffer (1991); Pincus et al. (2012)   \\
                                                                   & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
   Cloud amount  & Short name: CALIPSO   \\
                           & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\
                           & Reference: Chepfer et al. (2010); Cesana and Chepfer (2013)      \\
    \hline
 \multicolumn{2}{l}{$^{a}$Footnote text here.}
 \label{tab:obs}
 \end{tabular}
 \end{sidewaystable}

### 2020-07-04 Silvers_cfmip_extraTable.tex
changes to Silvers_cfmip.tex, minor changes to Silvers_cfmip_extraTable.tex, and Silvers_cfmip_CRE_SinglePanel.tex

We calculate feedbacks for the coupled experiments, and amip, as follows.     The difference in surface temperature is calculated 
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.   
The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
to years 1996-2015 (Is it correct that $T_2$ and $N_2$ correspond to different years?).

\begin{equation}
  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_1}
\end{equation}
\begin{equation}
  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
\end{equation}

>>>>

We calculate feedbacks for the coupled experiments, and amip, as follows.     The difference in surface temperature is calculated 
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.   
The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
the years used for $N$ and $T$ are the same.  $N_1$ and $T_1$ corresponds to years 101-150, while $N_2$ and $T_2$ corresponds
to years 1996-2015.

\begin{equation}
  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
\end{equation}
\begin{equation}
  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
\end{equation}
